---
title: "Untitled"
author: "Corinne"
date: "6/22/2020"
output: html_document
---

```{r setup, include = FALSE}
root <- 'D:/Research/_data/LISFLOOD'

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = root)

```


```{r packages, message = FALSE, warning = FALSE}
require(raster)
require(dplyr)
require(ggplot2); theme_set(theme_bw())

```

## Exercise 3
```{r}
## import data
d <- raster('./exercise3/Data_layers/maxdepth.asc')
v <- raster('./exercise3/Data_layers/maxVc.asc')

```

#### Physical risk assessment for people
$$ H_{people} = d(v+1.5) + DF $$
```{r}
## create the DF layer
DF <- (d > 0.25) | (v > 2)

## create the H_people layer
hazard_people <- d * (v+1.5) + DF

```

$$ R_1 = 2 E \left( \frac{SF_{area}}{100} \right) H_{people} \left( \frac{SF_{people}}{100} \right) $$
$$ R_2 = 2R_1 \left( \frac{H_{people}}{100} \right) $$
```{r}
## calculate expected number of injuries (R1)
### assume E = exposure = population (everyone is exposed), and assume SF_area = 9
pop <- raster('./exercise3/Data_layers/population.asc')
SF_area <- 9
SF_people <- raster('./exercise3/Data_layers/people_mobility.asc') + raster('./exercise3/Data_layers/people_old.asc')

R1 <- 2 * pop * (SF_area/100) * hazard_people * (SF_people/100)

## calculate expected number of fatalities (R2)
R2 <- 2 * R1 * (hazard_people/100)

```

## Physical risk assessment for buildings
```{r}
hazard_class <- v*0
# hazard_class[v == 0 & v*d == 0] <- 0
hazard_class[(v > 0 & v*d > 0 & v*d <= 3) | (v > 0 & v*d > 0 & v <= 2)] <- 1
hazard_class[v > 2 & v*d > 3 & v*d <= 7] <- 2
hazard_class[v > 2 & v*d > 7] <- 3

buildings <- raster('./exercise3/Data_layers/buildings.asc')
R_class_building <- mask(hazard_class, buildings, maskvalue = 0)

```

## Physical flood risk to infrastructure
```{r}
inundation <- mask(d > 0, d, maskvalue = 0) %>% 
  rasterToPolygons(dissolve = TRUE) %>% 
  st_as_sf
roads <- st_read('./exercise3/Data_layers/roads.shp') %>% 
  st_transform(st_crs(inundation))
flooded_roads <- st_intersection(roads, inundation)

```

## Economic flood risk to buildings
```{r}
depth_damage <- data.frame(depth.min = c(seq(0, 3, 0.3), seq(3.4, 4.9, 0.3)), 
                           depth.max = c(seq(0.3, 3, 0.3), seq(3.4, 4.9, 0.3), 100), 
                           structure = c(0, 15, 21, 26, 31, 36, 41, 45, 49, 52, 56, 59, 61, 64, 66, 68, 69), 
                           contents = c(0, 9, 12, 16, 19, 21, 24, 26, 28, 30, 32, 33, 35, 36, 36, 37, 37))
damage_structure <- reclassify(d, rcl = depth_damage[,-4])
damage_contents <- reclassify(d, rcl = depth_damage[,-3])

buildings_cost <- raster('./exercise3/Data_layers/buildings_cost.asc')
cost_structure <- buildings * buildings_cost * damage_structure/100
cost_contents <- buildings * buildings_cost * damage_contents/100
cost_total <- cost_structure + cost_contents

cellStats(cost_total, sum)

```

## Exercise 4

#### Creating a probabilistic flood hazard map
```{r}
## import data
data <- R.matlab::readMat('./exercise4/Exercise 4 data.mat')
depth <- data$water.depthBE
depth <- array(unlist(depth), dim = c(nrow(depth[[1]]), ncol(depth[[1]]), 100))

## create a probabilistic flood hazard map
pfhm <- apply(depth>0, c(1,2), sum)

```

#### Investigating the effect of spatial dependence
```{r}
## first, simulate the "worst-case" 1-in-100 year flood 
flow <- data$best.estimateQs

## find the flow in each channel with an RP of 100 years
flow %>% 
  apply(2, function(x) sort(x, decreasing = TRUE)) %>%
  cbind(100/(1:nrow(flow))) %>% 
  as.data.frame %>% 
  setNames(c('main', 'trib1', 'trib2', 'RP')) %>% 
  subset(RP == 10) %>% 
  select(-RP)

## run in lisflood -> import results
results <- raster('./exercise4/lisflood_data/results/res.max.asc')

## compare to the probabilistic model from above
pfhm.raster <- setValues(results, pfhm)                      
ggplot() + 
  geom_tile(data = as.data.frame(results > 0, xy = TRUE) %>% subset(layer), 
            aes(x = x, y = y, fill = 'Worst-Case'), alpha = 0.5) + 
  geom_tile(data = as.data.frame(pfhm.raster > 10, xy = TRUE) %>% subset(layer), 
            aes(x = x, y = y, fill = 'Spatial Dependence'), alpha = 0.5) + 
  scale_fill_manual(name = 'Model Type', values = c('green', 'blue')) + 
  coord_fixed(ratio = 1) + 
  theme_classic() + theme(axis.title = element_blank())

```

#### Estimating uncertainty
```{r}
depth.99 <- data$AE01BS
depth.99 <- array(unlist(depth.99), dim = c(nrow(depth.99[[1]]), ncol(depth.99[[1]]), 99))
flood.99 <- apply(depth.99 > 0, c(1,2), sum)
flood.raster <- setValues(results, flood.99)

river <- st_read('./exercise3/Data_layers/River.shp')

require(RColorBrewer)
ggplot() + 
  geom_tile(data = as.data.frame(flood.raster, xy = TRUE) %>% subset(res.max > 0),
            aes(x = x, y = y, fill = 'Highest 10%')) + 
  geom_tile(data = as.data.frame(flood.raster, xy = TRUE) %>% subset(res.max >= quantile(1:99, 0.1)),
            aes(x = x, y = y, fill = 'Middle 80%')) +
  geom_tile(data = as.data.frame(flood.raster, xy = TRUE) %>% subset(res.max >= quantile(1:99, 0.9)),
            aes(x = x, y = y, fill = 'Lowest 10%')) +
  geom_sf(data = river, size = 2, color = 'black') + 
  scale_fill_manual(name = 'Uncertainty',
                    breaks = c('Lowest 10%', 'Middle 80%', 'Highest 10%'), 
                    values = brewer.pal(4, 'Blues')[c(2,4,3)]) + 
  ggtitle('1-in-100 Year Flood Extent') + 
  # coord_fixed(ratio = 1) + 
  theme_classic() + theme(axis.title = element_blank())

```


## Exercise 5

#### flood prevention scenario A: floodwalls
```{r}
## modify original DEMs to account for floodwalls

## wall #1: north waterville
dem <- raster('./exercise5/A_floodwall/flood_valley_original.dem.asc')
# 424250:424450 %>% colFromX(object = dem)
x <- 27:30
# 198502:198702 %>% rowFromY(object = dem)
y <- 30:27

for (i in 1:4) {
  dem[y[i], x[i]] <- dem[y[i], x[i]] + 1
}
writeRaster(dem, './exercise5/A_floodwall/flood_valley_wall1.dem.asc', overwrite = TRUE)

## wall #2: north riverton
dem <- raster('./exercise5/A_floodwall/flood_valley_original.dem.asc')
# 425551:425751 %>% colFromX(object = dem) 
x <- 53:56
# 199101:198901 %>% rowFromY(object = dem)
y <- 19:22

for (i in 1:4) {
  dem[y[i], x[i]] <- dem[y[i], x[i]] + 1
}
writeRaster(dem, './exercise5/A_floodwall/flood_valley_wall2.dem.asc', overwrite = TRUE)

```

#### flood prevention scenario B: channel modification
```{r}
## deepening the channel
bed <- raster('./exercise5/B_channel_modification/flood_valley_original.bed.asc')
writeRaster(bed - 1, './exercise5/B_channel_modification/flood_valley_deeper.bed.asc', overwrite = TRUE)

## widening the channel
width <- raster('./exercise5/B_channel_modification/flood_valley_original.width.asc')
writeRaster(width * 2, './exercise5/B_channel_modification/flood_valley_wider.width.asc', overwrite = TRUE)

## creating an extra channel
dem <- raster('./exercise5/A_floodwall/flood_valley_original.dem.asc')
bed[28, 43:51] <- dem[28, 43:51] - 2
width[28, 43:51] <- 20
writeRaster(bed, './exercise5/B_channel_modification/flood_valley_extra.bed.asc', overwrite = TRUE)
writeRaster(width, './exercise5/B_channel_modification/flood_valley_extra.width.asc', overwrite = TRUE)

```

