---
title: "Untitled"
author: "Corinne"
date: "10/19/2020"
output: html_document
---

```{r setup, include = FALSE}
# rm(list=ls())

root <- 'D:/Research'

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = root)

```

```{r packages, message = FALSE, warning = FALSE}
require(ggplot2); theme_set(theme_classic())
require(sf)
require(raster)
require(reshape2)
require(dplyr)
require(tigris); options(tigris_use_cache = TRUE)
require(stringr)
require(lubridate)
require(RColorBrewer)
require(rnoaa); rnoaa_options(cache_messages = FALSE)
require(dataRetrieval)
require(glmnet)
require(GGally)
require(ncdf4)
require(velox)

```

```{r functions}
toNumber <- function(x) as.numeric(paste(x))

ggcolor <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

log_breaks <- function(min, max) rep(1:9, (max-min+1))*(10^rep(min:max, each = 9))

Mean <- function(x) mean(x, na.rm = TRUE)
Sum <- function(x) ifelse(nrow(x)>0, sum(x, na.rm = TRUE), NA)
Max <- function(x) max(x, na.rm = TRUE)
Min <- function(x) min(x, na.rm = TRUE)

## meters to feet conversion factor
mft <- 3.28084

```


**LISFLOOD parameter sensitivity tests**

* downstream boudnary condition: free vs. fixed
* Manning's roughness (floodplain): constant vs. spatially varying
* channel roughness
* dry/wet initial condition
* simulation length
* simulation timestep
* streambed depth
* streambed width
* DEM resolution
* unit hydrograph parameters

```{r}

```


**runoff vs. discharge comparison**

```{r}
## get catalog of historic events
inlet <- st_read('C:/Users/cbowers/Downloads/inlet/layers/globalwatershed.shp', quiet = TRUE)
inlet.point <- st_read('C:/Users/cbowers/Downloads/inlet/layers/globalwatershedpoint.shp', quiet = TRUE)
outlet <- st_read('C:/Users/cbowers/Downloads/outlet/layers/globalwatershed.shp', quiet = TRUE)
outlet.point <- st_read('C:/Users/cbowers/Downloads/outlet/layers/globalwatershedpoint.shp', quiet = TRUE)

gauge <- c(11464000, 11467000)
# gauge <- c(11463500, 11463682)
catalog <- generate_AR_catalog(outlet, gauge)
AR <- catalog %>% mutate(n.AR = 1:nrow(catalog))

```


```{r}
## find precipitation for each historic event
cl <- makeCluster(round(detectCores()*2/3))
registerDoSNOW(cl)
precip <- generate_precip(AR, catalog, n.precip = 100, dx = 0.05, precip.threshold = 0.5, plot = FALSE)
stopCluster(cl)

## compare simulated vs. recorded precip
precip.compare <- precip %>% 
  group_by(n.AR) %>% 
  summarize(precip_mean = mean(precip_mm), 
            precip_sd = sd(precip_mm),
            precip_lower = precip_mean - 2*precip_sd,
            precip_upper = precip_mean + 2*precip_sd) %>% 
  full_join(catalog %>% select(precip_obs = precip) %>% mutate(n.AR = 1:nrow(.)), by = 'n.AR')
ggplot(precip.compare) + 
  geom_point(aes(x = precip_obs, y = precip_mean)) + 
  geom_errorbar(aes(x = precip_obs, ymin = precip_lower, ymax = precip_upper), alpha = 0.25) + 
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed') + 
  ggtitle('Sonoma County Precipitation (mm)') + 
  labs(x = 'Observed', y = 'Simulated') + 
  scale_x_continuous(expand = expansion(mult = c(0, 0.05))) + scale_y_continuous(expand = c(0,0)) + 
  coord_fixed(ratio = 1, xlim = c(0, NA), y = c(0, NA))
ggsave('D:/Research/_plots/slides_precipplot.jpg', width = 5, height = 5)

ggplot(precip.compare) + 
  geom_point(aes(x = n.AR, y = precip_obs-precip_mean)) + 
  geom_hline(yintercept = 0, linetype = 'dashed') + 
  ggtitle('Precipitation Residuals') + 
  scale_x_continuous(expand = c(0,0)) + scale_y_continuous(expand = c(0,0)) + 
  labs(x = 'Storm Number', y = 'Observed - Simulated')
ggplot(precip.compare) + 
  geom_histogram(aes(x = precip_obs-precip_mean), bins = sqrt(nrow(AR)), color = 'black', fill = 'white') + 
  geom_vline(xintercept = 0, linetype = 'dashed') + 
  ggtitle('Precipitation Residuals') + 
  scale_x_continuous(expand = c(0,0)) + scale_y_continuous(expand = c(0,0)) + 
  labs(x = 'Observed - Simulated', y = 'Frequency of Occurrence')
ggsave('D:/Research/_plots/slides_preciphist.jpg', width = 5, height = 5)

```


```{r}
## find runoff for each historic event
runoff <- generate_runoff(precip, catalog, n.runoff = 100, plot = FALSE)

## get real storm-total discharge
param <- c('00060', '00065'); names(param) <- c('discharge_cfs', 'gageht_ft')
statcode <- c('00001', '00002', '00003', '00008'); names(statcode) <- c('max', 'min', 'mean', 'median')
site.discharge <- readNWISdv(gauge, parameterCd = param, statCd = statcode, startDate = '1980-01-01') %>% 
  renameNWISColumns() %>% 
  full_join(readNWISsite(gauge), by = 'site_no') %>% 
  dplyr::select(Flow, Date) %>% 
  group_by(Date) %>% 
  summarize(Flow = Mean(Flow))
for (ar in 1:nrow(catalog)) {
  datelist <- seq(ymd(catalog$start_day[ar]), ymd(catalog$end_day[ar]), 'days')
  catalog[ar, 'discharge_cfs'] <- site.discharge %>% 
    subset(Date %in% datelist) %>% 
    select(Flow) %>% 
    unlist %>% unname %>% Mean
  catalog[ar, 'discharge_m3s'] <- catalog[ar, 'discharge_cfs'] / mft^3
}
  
## find area of watershed (square miles)
# drainarea <- inlet$DRNAREA
# drainarea <- as.numeric(st_area(inlet))*(mft/5280)^2
drainarea <- mean(readNWISsite(gauge)$drain_area_va)

## compare simulated vs. recorded discharges
discharge.compare <- runoff %>% 
  mutate(discharge_cfs = (runoff_in/12) * (drainarea*5280^2) / (duration*60^2),
         discharge_m3s = (runoff_mm/1e3) * drainarea*(5280/mft)^2 / (duration*60^2)) %>% 
  group_by(n.AR) %>% 
  summarize(cfs_mean = mean(discharge_cfs), 
            cfs_sd = sd(discharge_cfs), 
            cfs_lower = cfs_mean - 2*cfs_sd,
            cfs_upper = cfs_mean + 2*cfs_sd,
            m3s_mean = mean(discharge_m3s), 
            m3s_sd = sd(discharge_m3s),
            m3s_lower = m3s_mean - 2*m3s_sd,
            m3s_upper = m3s_mean + 2*m3s_sd) %>% 
  full_join(catalog %>% select(discharge_cfs, discharge_m3s) %>% mutate(n.AR = 1:nrow(catalog)), ., by = 'n.AR')
ggplot(discharge.compare) + 
  geom_point(aes(x = discharge_cfs, y = cfs_mean)) + 
  geom_errorbar(aes(x = discharge_cfs, ymin = cfs_lower, ymax = cfs_upper), alpha = 0.25) + 
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed') + 
  ggtitle('Russian River Discharge (cfs)') + 
  labs(x = 'Observed', y = 'Simulated') + 
  scale_x_continuous(labels = scales::comma, expand = expansion(mult = c(0,0.05))) + 
  scale_y_continuous(labels = scales::comma, expand = expansion(mult = 0)) +
  coord_fixed(ratio = 1, xlim = c(0, 75000), ylim = c(0, 81000)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave('D:/Research/_plots/slides_runoffplot.jpg', width = 5, height = 5)

ggplot(discharge.compare) + 
  geom_point(aes(x = n.AR, y = discharge_cfs - cfs_mean)) + 
  geom_hline(yintercept = 0, linetype = 'dashed') + 
  ggtitle('Discharge Residuals') + 
  scale_x_continuous(expand = c(0,0)) + scale_y_continuous(expand = c(0,0)) + 
  labs(x = 'Storm Number', y = 'Observed - Simulated')
ggplot(discharge.compare) + 
  geom_histogram(aes(x = discharge_cfs - cfs_mean), bins = sqrt(nrow(AR)), color = 'black', fill = 'white') + 
  geom_vline(xintercept = 0, linetype = 'dashed') + 
  ggtitle('Discharge Residuals') + 
  scale_x_continuous(expand = c(0,0)) + scale_y_continuous(expand = c(0,0)) + 
  labs(x = 'Observed - Simulated', y = 'Frequency of Occurrence')
ggsave('D:/Research/_plots/slides_runoffhist.jpg', width = 5, height = 5)

```

```{r}
## look at the uncertainty in G(R) alone
runoff <- generate_runoff(data.frame(precip_mm = catalog$precip, 
                                     duration = catalog$duration,
                                     n.AR = 1:nrow(catalog), 
                                     n.precip = 1),
                          catalog, n.runoff = 100, plot = FALSE)

drainarea <- mean(readNWISsite(gauge)$drain_area_va)
discharge.compare <- runoff %>% 
  mutate(discharge_cfs = (runoff_in/12) * (drainarea*5280^2) / (duration*60^2),
         discharge_m3s = (runoff_mm/1e3) * drainarea*(5280/mft)^2 / (duration*60^2)) %>% 
  group_by(n.AR) %>% 
  summarize(cfs_mean = mean(discharge_cfs), 
            cfs_sd = sd(discharge_cfs), 
            cfs_lower = cfs_mean - 2*cfs_sd,
            cfs_upper = cfs_mean + 2*cfs_sd,
            m3s_mean = mean(discharge_m3s), 
            m3s_sd = sd(discharge_m3s),
            m3s_lower = m3s_mean - 2*m3s_sd,
            m3s_upper = m3s_mean + 2*m3s_sd) %>% 
  full_join(catalog %>% select(discharge_cfs, discharge_m3s) %>% mutate(n.AR = 1:nrow(catalog)), ., by = 'n.AR')
ggplot(discharge.compare) + 
  geom_point(aes(x = discharge_cfs, y = cfs_mean)) + 
  geom_errorbar(aes(x = discharge_cfs, ymin = cfs_lower, ymax = cfs_upper), alpha = 0.25) + 
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed') + 
  ggtitle('Russian River Discharge (cfs)') + 
  labs(x = 'Observed', y = 'Simulated') + 
  scale_x_continuous(labels = scales::comma, expand = expansion(mult = c(0,0.05))) + 
  scale_y_continuous(labels = scales::comma, expand = expansion(mult = 0)) +
  coord_fixed(ratio = 1, xlim = c(0, 75000), ylim = c(0, 81000)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave('D:/Research/_plots/slides_runoffplot.jpg', width = 5, height = 5)

ggplot(discharge.compare) + 
  geom_histogram(aes(x = discharge_cfs - cfs_mean), bins = sqrt(nrow(AR)), color = 'black', fill = 'white') + 
  geom_vline(xintercept = 0, linetype = 'dashed') + 
  ggtitle('Discharge Residuals') + 
  scale_x_continuous(expand = c(0,0)) + scale_y_continuous(expand = c(0,0)) + 
  labs(x = 'Observed - Simulated', y = 'Frequency of Occurrence')
ggsave('D:/Research/_plots/slides_runoffhist.jpg', width = 5, height = 5)

```

```{r}
runoff.compare <- runoff %>% 
  group_by(n.AR) %>% 
  summarize(in_mean = mean(runoff_in), 
            in_sd = sd(runoff_in), 
            in_lower = in_mean - 2*in_sd, 
            in_upper = in_mean + 2*in_sd,
            mm_mean = mean(runoff_mm), 
            mm_sd = sd(runoff_mm),
            mm_lower = mm_mean - 2*mm_sd,
            mm_upper = mm_mean + 2*mm_sd) %>% 
  full_join(catalog %>% select(runoff) %>% mutate(n.AR = 1:nrow(.)), by = 'n.AR')
ggplot(runoff.compare) + 
  geom_point(aes(x = runoff, y = mm_mean)) + 
  geom_errorbar(aes(x = runoff, ymin = mm_lower, ymax = mm_upper), alpha = 0.25) + 
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed') + 
  ggtitle('Russian River Runoff (mm)') + 
  labs(x = 'Observed', y = 'Simulated') + 
  coord_fixed(ratio = 1, xlim = c(0,NA), ylim = c(0,NA))

```

**LISFLOOD unit hydrograph**

```{r}
# vec <- c(seq(0.1,0.9,0.1), seq(1, 19, 1), seq(20, 98, 2.5), seq(100, 395, 5), seq(400, 990, 10), 
#          seq(1000, 1990, 25), seq(2000, 4900, 50), seq(5000, 7000, 100))

runoff %>% 
  group_by(n.AR) %>% 
  summarize(duration = mean(duration),
            mm_mean = mean(runoff_mm),
            mm_sd = sd(runoff_mm),
            mm_lower = mm_mean - 2*mm_sd,
            mm_upper = mm_mean + 2*mm_sd) %>% 
ggplot() + 
  geom_hline(yintercept = 0, linetype = 'dashed') + 
  geom_point(aes(x = duration, y = mm_mean)) + 
  geom_errorbar(aes(x = duration, ymin = mm_lower, ymax = mm_upper), alpha = 0.25) + 
  scale_x_continuous(expand = c(0,0)) + 
  ggtitle('Duration vs. Runoff Total') + 
  labs(x = 'Storm Duration (hrs)', y = 'Storm Total Runoff (mm)')
ggsave('D:/Research/_plots/duration_runoff.jpg', width = 6.5, height = 5)

```

```{r}
## get unit hydrograph parameters ## 

## step 1: go through every graph and pick the ones that look good
## iv starts in mid-1987 (row 98)
for (c in 98:nrow(catalog)) {
  ## find start of precipitation
  data <- data.frame(date = seq(ymd(cat$start[c]) - days(4), ymd(cat$end[c]) + days(6), 'days'))
  for (i in 1:nrow(data)) {
    d <- ymd(data$date[i])
    cpc_precip <- cpc_prcp(d)
    cpc_precip$lon <- cpc_precip$lon-360
    cpc_precip <- suppressWarnings(rasterFromXYZ(cpc_precip, crs = st_crs(california)$proj4string))
    data$precip[i] <- velox(cpc_precip)$extract(aoi, small = TRUE) %>% lapply(mean) %>% unlist
  }
  if (sum(data$precip > 1) > 0) {
    data <- data[which(data$precip > 1)[1]:nrow(data),]

    ## find tp & Qp
    flow <- readNWISdata(sites = gauge, parameterCd = param,
                         startDate = data$date[1], endDate = data$date[nrow(data)],
                         service = 'iv', tz = 'America/Los_Angeles') %>% 
      renameNWISColumns %>% 
      mutate(Flow = Flow_Inst, Date = dateTime)
    temp <- flow %>% 
      group_by(site_no) %>% 
      summarize(tp = toNumber(difftime(Date[which.max(Flow)], Date[1], units = 'secs')),
                Qp = max(Flow))

    ## check to see if it looks like a "nice" storm
    fit1 <- flow %>%
      subset(site_no == gauge[1]) %>%
      mutate(t = toNumber(difftime(Date, Date[1], units = 'secs')/toNumber(temp[1,'tp'])),
             q = (Flow-Min(Flow))/(toNumber(temp[1,'Qp'])-Min(Flow)),
             site_no = gauge[1]) %>%
      select(site_no, t, q)
    fit2 <- flow %>%
      subset(site_no == gauge[2]) %>%
      mutate(t = toNumber(difftime(Date, Date[1], units = 'secs')/toNumber(temp[2,'tp'])),
             q = (Flow-Min(Flow))/(toNumber(temp[2,'Qp'])-Min(Flow)),
             site_no = gauge[2]) %>%
      select(site_no, t, q)
    fit <- rbind(fit1, fit2)
    g <- ggplot(fit) +
      geom_line(aes(x = t, y = q, color = factor(site_no), group = factor(site_no))) +
      ggtitle(paste0('ID = ', c))
    print(g)
  }
}
keep <- c(100,104,110,111,113,117,118,119,120,122,129,131,138,
          153,155,160,161,163,172,173,177,182,184,
          207,216,222,227,232,235,241,
          252,253,254,255,260,262,263,268,269,272,274,280,281,282,286,289,296,298,
          308,311,318,320,326,331,
          353,359,362,372,379,384,395,
          406,409,417,419,421,427,429,430,432,442,446,449,450,451,455,460,463,465,466)

## step 2: get m by fitting nonlinear gamma distribution
hydrograph <- data.frame(site_no = NA, tp = NA, Qp = NA, m = NA, n.AR = NA)[-1,]
pb <- txtProgressBar(min = 0, max = nrow(catalog), style = 3)
for (c in keep) {
  ## find start of precipitation
  data <- data.frame(date = seq(ymd(cat$start[c]) - days(4), ymd(cat$end[c]) + days(6), 'days'))
  for (i in 1:nrow(data)) {
    d <- ymd(data$date[i])
    cpc_precip <- cpc_prcp(d)
    cpc_precip$lon <- cpc_precip$lon-360
    cpc_precip <- suppressWarnings(rasterFromXYZ(cpc_precip, crs = st_crs(california)$proj4string))
    data$precip[i] <- velox(cpc_precip)$extract(aoi, small = TRUE) %>% lapply(mean) %>% unlist
  }
  data <- data[which(data$precip > 0)[1]:nrow(data),]

  ## find tp & Qp
  flow <- readNWISdata(sites = gauge, parameterCd = param,
                       startDate = data$date[1], endDate = data$date[nrow(data)],
                       service = 'iv', tz = 'America/Los_Angeles') %>% 
    renameNWISColumns %>% 
    rename(Flow = Flow_Inst, Date = dateTime)
  temp <- flow %>% 
    group_by(site_no) %>% 
    summarize(tp = toNumber(difftime(Date[which.max(Flow)], Date[1], units = 'secs')),
              Qp = max(Flow)) %>% 
    mutate(m = NA, n.AR = c)
  
  ## find m 
  for (id in 1:nrow(temp)) {
    if (!is.na(temp$Qp[id])) {
      fit <- flow %>%
        subset(site_no == gauge[id]) %>%
        mutate(t = toNumber(difftime(Date, Date[1], units = 'secs')/toNumber(temp[id,'tp'])),
               q = (Flow-Min(Flow)) / (toNumber(temp[id,'Qp'])-Min(Flow)),
               site_no = gauge[id]) %>% 
        select(site_no, t, q)
      model <- nls(q ~ exp(m*(1-t)) * t^m, data = fit, start = list(m = 3.7), control = list(maxiter = 500))
      temp$m[id] <- coef(model)
      # g <- ggplot(data = fit) +
      #   geom_line(aes(x = t, y = q)) +
      #   geom_line(aes(x = t, y = predict(model, fit)), color = 'red') + 
      #   ggtitle(paste0('ID = ', c, ' & Site = ', temp$site_no[id]))
      # print(g)
    }
  }
  hydrograph <- rbind(hydrograph, temp)
  setTxtProgressBar(pb, c)
}
hydrograph <- hydrograph[!is.na(hydrograph$Qp),]
hydrograph_save <- hydrograph

```


```{r}
## find relationship between PARRA parameters & hydrograph parameters ## 

hydrograph <- hydrograph_save %>% 
  full_join(catalog %>% mutate(n.AR = 1:nrow(.)), by = 'n.AR') %>%
  pivot_wider(names_from = site_no, values_from = c(tp, Qp, m)) %>% 
  mutate(tp = rowMeans(cbind(tp_11464000, tp_11467000)/60^2),
         Qp = rowMeans(cbind(Qp_11464000, Qp_11467000)),
         m = rowMeans(cbind(m_11464000, m_11467000))) %>% 
  select(-tp_11464000, -tp_11467000, -tp_NA,
         -Qp_11464000, -Qp_11467000, -Qp_NA,
         -m_11464000, -m_11467000, -m_NA)

## tp vs. duration
ggplot(hydrograph) + 
  geom_point(aes(x = duration, y = tp)) + 
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed') + 
  # ggtitle(expression(paste('Duration vs. ', t[p]))) + 
  labs(x = 'Storm Duration (hrs)', y = 'Time to Peak Discharge (hrs)') + 
  scale_x_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  scale_y_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  coord_fixed(ratio = 1)
ggsave('D:/Research/_plots/slides_tp.jpg', width = 5, height = 5)

## tp vs. precip & runoff
ggplot(hydrograph) + 
  geom_point(aes(x = IVT_max, y = tp)) + 
  scale_x_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  scale_y_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  labs(x = 'Max IVT (kg/m/s)', y = 'Time to Peak Discharge (hrs)')
ggplot(hydrograph) + 
  geom_point(aes(x = precip, y = tp)) + 
  scale_x_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  scale_y_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  labs(x = 'Precipitation (mm)', y = 'Time to Peak Discharge (hrs)')
ggplot(hydrograph) + 
  geom_point(aes(x = runoff, y = tp)) + 
  scale_x_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  scale_y_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  labs(x = 'Runoff (mm)', y = 'Time to Peak Discharge (hrs)')

## daily max vs. daily mean discharge
for (ar in 1:nrow(catalog)) {
  datelist <- seq(ymd(catalog$start_day[ar]), ymd(catalog$end_day[ar]), 'days')
  catalog[ar, 'discharge_mean'] <- site.discharge %>% 
    subset(Date %in% datelist) %>% 
    select(Flow) %>% 
    unlist %>% unname %>% Mean
  catalog[ar, 'discharge_max'] <- site.discharge %>% 
    subset(Date %in% datelist) %>% 
    select(Flow) %>% 
    unlist %>% unname %>% Max
}
ggplot(catalog) + 
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed') +
  geom_abline(slope = 2, intercept = 0, linetype = 'dotted') + 
  geom_point(aes(x = discharge_mean, y = discharge_max, color = duration)) + 
  scale_color_gradientn(colors = c('darkblue', 'red', 'goldenrod')) + 
  scale_x_continuous(labels = scales::comma, expand = expansion(mult = c(0, 0.05))) + 
  scale_y_continuous(labels = scales::comma, expand = expansion(mult = c(0, 0.05))) + 
  labs(x = 'Mean Discharge (cfs)', y = 'Max Discharge (cfs)') + 
  coord_fixed(ratio = 1)
ggsave('D:/Research/_plots/slides_meanmaxdischarge.jpg', width = 5, height = 5)

## Qp vs. daily mean discharge
ggplot() + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)), color = 'grey60') + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)*2), linetype = 'dashed', color = 'grey60') + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)*5), linetype = 'dashed', color = 'grey60') + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)*10), color = 'grey60') + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)*20), linetype = 'dashed', color = 'grey60') + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)*50), linetype = 'dashed', color = 'grey60') + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)*100), color = 'grey60') + 
  geom_point(data = hydrograph, aes(x = discharge_mean, y = Qp, color = duration)) + 
  scale_color_gradientn(colors = c('darkblue', 'red', 'goldenrod')) + 
  scale_x_continuous(labels = scales::comma, expand = expansion(mult = c(0, 0.05))) + 
  scale_y_continuous(labels = scales::comma, expand = expansion(mult = c(0, 0.05))) + 
  labs(x = 'Mean Discharge (cfs)', y = 'Peak Discharge (cfs)') + 
  coord_fixed(ratio = 1, 
              xlim = c(Min(hydrograph[,c('discharge_mean', 'Qp')]), 
                       Max(hydrograph[,c('discharge_mean', 'Qp')])),
              ylim = c(Min(hydrograph[,c('discharge_mean', 'Qp')]), 
                       Max(hydrograph[,c('discharge_mean', 'Qp')])))
ggplot() + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)), color = 'grey60') + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)*2), linetype = 'dashed', color = 'grey60') + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)*5), linetype = 'dashed', color = 'grey60') + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)*10), color = 'grey60') + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)*20), linetype = 'dashed', color = 'grey60') + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)*50), linetype = 'dashed', color = 'grey60') + 
  geom_line(aes(x = c(1,1e6), y = c(1,1e6)*100), color = 'grey60') + 
  geom_point(data = hydrograph, aes(x = discharge_mean, y = Qp, color = duration)) + 
  scale_color_gradientn(colors = c('darkblue', 'red', 'goldenrod')) + 
  scale_x_log10(labels = scales::comma, expand = expansion(mult = c(0, 0.05))) + 
  scale_y_log10(labels = scales::comma, expand = expansion(mult = c(0, 0.05))) + 
  annotation_logticks() + 
  labs(x = 'Mean Discharge (cfs)', y = 'Peak Discharge (cfs)') + 
  coord_fixed(ratio = 1, 
              xlim = c(Min(hydrograph[,c('discharge_mean', 'Qp')]), 
                       Max(hydrograph[,c('discharge_mean', 'Qp')])),
              ylim = c(Min(hydrograph[,c('discharge_mean', 'Qp')]), 
                       Max(hydrograph[,c('discharge_mean', 'Qp')])))
ggsave('D:/Research/_plots/slides_logdischarge.jpg', height = 5)

lm(Qp ~ runoff, data = hydrograph) %>% summary


```


```{r}
## check linear predictive power
tp.lasso <- 
  cv.glmnet(x = hydrograph %>% subset(!is.na(tp)) %>% select(IVT_max, duration, precip, runoff) %>% as.matrix, 
            y = hydrograph %>% subset(!is.na(tp)) %>% select(tp) %>% unlist,
            family = 'gaussian', alpha = 1,
            standardize = TRUE,
            nlambda = 1e3, lambda.min.ratio = 1e-5,
            nfolds = 10)
coef(tp.lasso, s = tp.lasso$lambda.1se)
coef(tp.lasso, s = tp.lasso$lambda.min)
lm(tp ~ duration + precip, data = hydrograph) %>% summary

Qp.lasso <- 
  cv.glmnet(x = hydrograph %>% subset(!is.na(tp)) %>% select(IVT_max, duration, precip, runoff) %>% as.matrix, 
            y = hydrograph %>% subset(!is.na(tp)) %>% select(Qp) %>% unlist,
            family = 'gaussian', alpha = 1,
            standardize = TRUE,
            nlambda = 1e3, lambda.min.ratio = 1e-5,
            nfolds = 10)
coef(Qp.lasso, s = Qp.lasso$lambda.1se)
coef(Qp.lasso, s = Qp.lasso$lambda.min)
lm(Qp ~ IVT_max + precip + runoff, data = hydrograph) %>% summary

ggplot(hydrograph) + 
  geom_point(aes(x = runoff, y = Qp)) + 
  scale_x_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  scale_y_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  labs(x = 'Runoff (mm)', y = 'Peak Discharge (cfs)')

ggpairs(hydrograph %>% select(IVT_max, duration, precip, runoff, tp, Qp), 
        progress = FALSE) + 
  theme_bw() + 
  scale_x_continuous(labels = scales::comma) + scale_y_continuous(labels = scales::comma) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 0.75))
  
```

```{r}
## test seasonality & soil moisture effects on tp ##

## open soil moisture file
soil_nc <- nc_open('./_data/soilmoisture/NOAA/soilw.mon.mean.v2.nc')
soil_lat <- ncvar_get(soil_nc, 'lat')
soil_lon <- ncvar_get(soil_nc, 'lon') - 180
soil_time <- ymd('1800-01-01') + days(ncvar_get(soil_nc, 'time'))
soil_time <- data.frame(month = month(soil_time), year = year(soil_time))
soil <- ncvar_get(soil_nc, 'soilw')
nc_close(soil_nc)

catalog$SM <- NA
pb <- txtProgressBar(min = 0, max = nrow(catalog), style = 3)
for (ar in 1:nrow(catalog)) {
  start <- ymd(catalog$start_day[ar]) - days(1)
  end <- ymd(catalog$end_day[ar]) + days(1)
  SM_stack <- raster::stack()
  monthrecord <- ifelse(month(start) <= month(end),
                        length(month(start):month(end)),
                        length((month(start)-12):month(end))) - 1
  startmonth <- ymd(paste(year(start), month(start), '1', sep = '-'))
  for (i in 0:monthrecord) {
    mo <- month(startmonth + months(i))
    yr <- year(startmonth + months(i))
    index <- (1:nrow(soil_time))[soil_time$month == mo & soil_time$year == yr]
    SM_raster <- raster(t(soil[,,index]), xmn = min(soil_lon), xmx = max(soil_lon), 
                        ymn = min(soil_lat), ymx = max(soil_lat))
    SM_stack <- raster::stack(SM_stack, SM_raster)
  }
  SM_avg <- mean(SM_stack)
  crs(SM_avg) <- projection(california)
  catalog$SM[ar] <- velox(SM_avg)$extract(aoi) %>% lapply(mean) %>% unlist
  setTxtProgressBar(pb, ar)
}
catalog$SM <- (catalog$SM - mean(catalog$SM)) / sd(catalog$SM)

catalog$wateryear <- ifelse(month(catalog$start) %in% 10:12, year(catalog$start)+1, year(catalog$start))
catalog$seasonlength <- as.numeric(ymd(catalog$start_day) - ymd(paste0(catalog$wateryear-1, '-10-1')))

hydrograph <- hydrograph_save %>% 
  full_join(catalog %>% mutate(n.AR = 1:nrow(.)), by = 'n.AR') %>%
  pivot_wider(names_from = site_no, values_from = c(tp, Qp, m)) %>% 
  mutate(tp = rowMeans(cbind(tp_11464000, tp_11467000)/60^2),
         Qp = rowMeans(cbind(Qp_11464000, Qp_11467000)),
         m = rowMeans(cbind(m_11464000, m_11467000))) %>% 
  select(-tp_11464000, -tp_11467000, -tp_NA,
         -Qp_11464000, -Qp_11467000, -Qp_NA,
         -m_11464000, -m_11467000, -m_NA)
ggplot(hydrograph) + 
  geom_point(aes(x = SM, y = tp/60^2)) + 
  scale_x_continuous(expand = c(0.01,0.01)) + 
  scale_y_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  labs(x = 'Normalized Soil Moisture Anomaly', y = 'Time to Peak Discharge (hrs)')
ggplot(hydrograph) + 
  geom_point(aes(x = seasonlength, y = tp/60^2)) + 
  scale_x_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  scale_y_continuous(limits = c(0,NA), expand = c(0.01,0.01)) + 
  labs(x = 'Days since Water Year Start', y = 'Time to Peak Discharge (hrs)')

ggpairs(hydrograph %>% subset(!is.na(tp)) %>% mutate(tp = tp/60^2) %>% select(SM, seasonlength, tp), 
        progress = FALSE) + theme_bw()

```






```{r}
generate_inundation <- function(fileloc, dem, river, lulc, parname, bciname, runoff, drainarea, 
                                tp = 48*3600, m = 4, baseflow = 2, simlength = 86400*10, plot = TRUE) {
  ## convert runoff to discharge
  runoff <- runoff %>% mutate(discharge_m3s = runoff_mm/1e3 * drainarea / duration / 3600)
  
  ## set up LISFLOOD simulation
  raster.list <- write_lisflood_rasters(fileloc, dem, river, lulc, parname, bciname)
  par <- raster.list[[1]]; edge.in <- raster.list[[2]]; edge.out <- raster.list[[3]]
  cmd <- paste0('cd ', fileloc, ' & lisflood ', parname, '.par')
  
  ## define write_lisflood_files function
  write_lisflood_files <- function(i, par, fileloc, parname, bciname, runoff, tp, m, baseflow, simlength) {
    ## set up hydrograph variables
    t <- seq(0, simlength, 360)
    baseflow <- baseflow / 100  #m2/s
    
    ## create hydrograph
    Qp <- runoff[i,'discharge_m3s'] / 100  #m2/s
    q <- apply(cbind(exp(m*(1-t/tp)) * (t/tp)^m * Qp, rep(baseflow, length(t))), 1, max)
    
    ## write .bdy file
    bdy <- matrix(c('LISFLOOD', NA, paste0('flow', i), NA, length(t), 'seconds'), 
                  byrow = TRUE, ncol = 2)
    bdy <- rbind(bdy, cbind(q, t))
    write.table(bdy, file = paste0(fileloc, 'flow', i, '.bdy'), 
                row.names = FALSE, col.names = FALSE, quote = FALSE, sep = '\t', na = '')
    
    ## edit .par and .bci file
    par[1,] <- c('resroot', paste0('test', i))  #prefix name on all results files
    par[15,] <- c('bdyfile', paste0('flow', i, '.bdy'))
    write.table(par, paste0(fileloc, parname, '.par'),
                row.names = FALSE, col.names = FALSE, quote = FALSE, sep = '\t', na = '')
    
    bci <- data.frame(matrix(c('N', min(edge.in$x), max(edge.in$x), 'QVAR', paste0('flow', i),
                               'W', min(edge.out$y), max(edge.out$y), 'FREE', NA),
                             nrow = 2, byrow = TRUE))
    write.table(bci, file = paste0(fileloc, bciname, '.bci'), 
                row.names = FALSE, col.names = FALSE, quote = FALSE, sep = '\t')
    
  }

  pb <- txtProgressBar(min = 0, max = nrow(runoff), style = 3)
  progress <- function(n) setTxtProgressBar(pb, n)
  opts <- list(progress = progress)
  
  inundation <- 
    foreach (i = 1:nrow(runoff),
             .packages = 'raster',
             .options.snow = opts) %dopar% {
      ## define input files
      write_lisflood_files(i, par, fileloc, parname, bciname, runoff, tp, m, baseflow, simlength)
      
      ## run LISFLOOD
      setwd(fileloc)
      shell(shQuote(cmd, type = 'cmd'))
  
      ## save results to raster brick
      raster(paste0(fileloc, 'results/test', i, '.max'))
    }

  inundation <- do.call('stack', inundation)
  crs(inundation) <- crs(dem)
  return(inundation)
}

inundation <- 
  generate_inundation(
    fileloc = 'C:/Users/cbowers/Desktop/LISFLOOD/sonoma/', 
    dem = dem, river = hydropoly_rr, lulc = lulc.n, 
    parname = 'grid', bciname = 'grid', 
    runoff = runoff, 
    drainarea = inlet$DRNAREA, 
    plot = FALSE
  )

```

