---
title: "Untitled"
author: "Corinne"
date: "1/8/2021"
output: html_document
---

```{r setup, include = FALSE}
root <- 'D:/Research'

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = root)

```

```{r packages, message = FALSE, warning = FALSE}
require(dataRetrieval)
require(sf)
require(tigris)
require(raster)
require(FedData)
require(lubridate)
require(pracma)
require(RColorBrewer)
require(tidyverse); theme_set(theme_classic())
require(plotly)

```

```{r functions}
toNumber <- function(x) as.numeric(paste(x))

ggcolor <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

log_breaks <- function(min, max) rep(1:9, (max-min+1))*(10^rep(min:max, each = 9))

Mean <- function(x) mean(x, na.rm = TRUE)
Sum <- function(x) sum(x, na.rm = TRUE)
Max <- function(x) max(x, na.rm = TRUE)
Min <- function(x) min(x, na.rm = TRUE)

plot.raster <- function(x) x %>% as.data.frame(xy = TRUE) %>% setNames(c('x', 'y', 'value')) 
sum.na <- function(x) sum(is.na(x))

## meters to feet conversion factor
mft <- 3.28084

```

```{r geography}
## EPSG codes for setting CRS
NAD <- 4269
albers <- 3310

california <- counties(state = 'CA')
sonoma <- tracts(state = 'CA', county = 'Sonoma')

russian <- st_read('./_gis/California/_hydrology/nhd_majorrivers/MajorRivers.shp', quiet = TRUE) %>% 
  st_zm(st_transform(albers)) %>% 
  subset(grepl('Russian', GNIS_Name))
wbd12 <- st_read('./_gis/California/_floodhazard/WBD_18_HU2_Shape/Shape/WBDHU12.shp', quiet = TRUE)

```

ArcGIS vignette: 

* download Hydro DEMs from SonomaVegMap: http://sonomavegmap.org/data-downloads/
* combine in ArcGIS using the Mosaic to New Raster tool
  + new raster name = SonomaVegMap
  + spatial reference = NAD_1983_2011_StatePlane_California_II_FIPS_0402_US_Feet
  + pixel type = 32-bit float
  + cell size = N/A (native resolution = 3 feet)
  + bands = 1
  + mosaic operator = blend
  + environment: turn off build pyramids, turn off raster statistics, 
    resample = bilinear, parallel processing factor = 5
    
* open TopoBathy: https://www.arcgis.com/home/item.html?id=c753e5bfadb54d46b69c3e68922483bc
* download ocean elevations
  + used aoi.shp as a guide & downloaded lower-left corner @ 10m elevation 
    (has to be under 5000x5000)

```{r}
## define CA zone 2 projection (6417 = meters, 6418 = US feet)
crs_dem <- st_crs(6417)

## define area of interest (aoi)
ext <- extent(1895000, 1935000, 579500, 616500)
aoi <- ext %>% as('SpatialPolygons') %>% st_as_sf %>% st_set_crs(6417)

## create blank raster with desired resolution
blank <- raster(ext, resolution = c(40,40), crs = projection(aoi))

## load SonomaVegMap file (takes about half an hour)
## horizontal: resolution = 3x3 feet, units = feet
## vertical: RMSE = 0.03 meters (see metadata), units = feet 
hydro <- raster('D:/Research/_gis/watersheds/SonomaVegMap_temp.tif') 
hydro <- hydro %>% aggregate(10) %>% projectRaster(blank)

## convert vertical units from feet to meters
dem.hydro <- hydro / mft

## check vertical units
# aoi %>% 
#   st_sample(10) %>% st_sf %>% 
#   elevatr::get_elev_point(.) %>% 
#   mutate(hydro = terra::extract(rast(temp2), st_coordinates(.)) %>% unlist %>% unname) %>% 
#   mutate(hydro_m = hydro / mft)

## load topobathy file for ocean elevation
topobathy <- raster('C:/Users/cbowers/Desktop/topobathy.tif') %>% 
  projectRaster(blank)

## check topobathy location
# ggplot() +
#   geom_raster(data = raster.df(topobathy) %>% filter(!is.na(value)),
#               aes(x=x, y=y), fill = 'blue') +
#   geom_raster(data = raster.df(dem) %>% filter(!is.na(value)),
#               aes(x=x, y=y), fill = 'red', alpha = 0.5) +
#   coord_sf(crs = crs_dem)

## check topobathy elevation
# raster.df(topobathy) %>% rename(topobathy = value) %>% 
#   left_join(raster.df(dem) %>% rename(dem = value), by = c('x', 'y')) %>% 
#   filter(!is.na(topobathy) & !is.na(dem)) %>% 
#   ggplot() + geom_point(aes(x = dem, y = topobathy), color = 'grey70') + geom_parity()
  
## add topobathy file to dem
dem <- dem.hydro %>% overlay(topobathy, fun = function(x,y) ifelse(is.na(x), y, x))

## save out
save(hydro, dem.hydro, dem, file = 'C:/Users/cbowers/Desktop/dem_save.Rdata')
writeRaster(dem, format = 'ascii', overwrite = TRUE,
            filename = 'C:/Users/cbowers/Desktop/LISFLOOD/new_rasters/russian.dem.asc')

```

```{r}
## check new DEM
load('C:/Users/cbowers/Desktop/buildings.Rdata')
res.buildings <- res.buildings %>% st_transform(crs_dem) %>% st_crop(aoi)

elev <- sample(1:nrow(res.buildings), size = 100) %>% 
  elevatr::get_elev_point(res.buildings[.,]) %>% 
  mutate(dem = dem %>% rast %>% 
           terra::extract(., st_coordinates(elev)) %>% 
           unlist %>% unname)
ggplot(elev) + 
  geom_point(aes(x = elevation, y = dem)) + 
  scale_x_origin() + scale_y_origin() + geom_parity() + coord_fixed()

```

```{r}
## step 2) get the channel width 
hydropoly <- 
  st_read('D:/Research/_gis/California/_hydrology/NHD_H_California_State_GDB/NHD_H_California_State_GDB.gdb',
          layer = 'NHDArea', quiet = TRUE) %>% st_transform(crs_dem)
fcode <- 
  st_read('D:/Research/_gis/California/_hydrology/NHD_H_California_State_GDB/NHD_H_California_State_GDB.gdb', 
          layer = 'NHDFCode', quiet = TRUE)
hydropoly_rr <- hydropoly %>% 
  left_join(fcode %>% select('FCODE', 'DESCRIPTION'), by = c('FCode' = 'FCODE')) %>% 
  subset(grepl('Stream/River', DESCRIPTION)) %>% 
  subset(row.names(.) == '2104') %>%  #get Russian River only
  sfheaders::sf_remove_holes(.) %>% 
  st_intersection(st_transform(wbd12, crs_dem)) %>% 
  mutate(feature_id = row.names(.)) %>% 
  subset(!(feature_id %in% c('2104', '2104.11', '2104.12', '2104.20'))) %>% 
  select(feature_id, Shape) 

hydropoly_rr <- hydropoly_rr %>%
  filter(feature_id %in% c('2104.16', '2104.17')) %>% 
  st_union %>% st_sf %>%
  transmute(feature_id = '2104.17', Shape = geometry) %>%
  st_drop_geometry %>%
  rbind(hydropoly_rr %>% filter(!(feature_id %in% c('2104.16', '2104.17')))) %>%
  st_sf %>% 
  st_crop(extent(blank)) %>% 
  st_cast('MULTIPOLYGON') %>% st_cast('POLYGON') %>% 
  mutate(feature_id = row.names(.)) %>% 
  filter(feature_id != '2104.14') %>% 
  mutate(AREA = st_area(.), 
       PERIMETER = lwgeom::st_perimeter(.),
       WIDTH = 2*AREA/PERIMETER)

width <- rasterize(x = hydropoly_rr %>% st_cast(to = 'MULTILINESTRING'), y = blank, field = 'WIDTH')

## get boundary edges for .bci file
width.df <- as.data.frame(width, xy = TRUE) %>% subset(!is.na(layer))
edge.in <- width.df[which(width.df$y == max(width.df$y)),]
edge.out <- width.df[which(width.df$x == min(width.df$x)),]

# require(leaflet)
# require(mapboxapi)
# temp <- hydropoly_rr %>% st_transform(st_crs(sonoma))
# leaflet(temp) %>%
#   addMapboxTiles(style_id = "light-v9", username = "mapbox") %>%
#   addPolygons(label = ~feature_id)
 
## save out
writeRaster(width, format = 'ascii', overwrite = TRUE, 
            filename = 'C:/Users/cbowers/Desktop/LISFLOOD/new_rasters/russian.width.asc')

```

```{r}
## step 3) get the floodplain roughness

## get LULC codes
lulc <- raster('D:/Research/_gis/USA/_landcover/NLCD_2016_Land_Cover_L48_20190424/NLCD_2016_Land_Cover_L48_20190424.img')
lulc.att <- lulc@data@attributes[[1]]
lulc.n <- FedData::get_nlcd(blank, label = 'value')
vals <- unique(lulc.n[])

## decide on roughness values for floodplain
manning <- readxl::read_xlsx('C:/Users/cbowers/Desktop/LISFLOOD/lisflood runs.xlsx', 
                     sheet = 3, skip = 2, col_names = FALSE) %>% 
  setNames(c('name', 'code', 'KS', 'KS_min', 'KS_max', 'JSH', 'HECRAS', 'MWR')) %>% 
  mutate(name = factor(name, levels = rev(name)))
ggplot(manning) + 
  geom_point(aes(x = name, y = KS, color = 'KS', shape = 'KS'), size = 3) + 
  # geom_errorbar(aes(x = name, ymin = KS_min, ymax = KS_max, color = 'KS'), width = 0.25) + 
  geom_segment(aes(x = name, xend = name, y = KS_min, yend = KS_max, color = 'KS'), size = 2, alpha = 0.25) + 
  # geom_point(aes(x = name, y = JSH, color = 'JSH', shape = 'JSH'), size = 3) + 
  geom_point(aes(x = name, y = HECRAS, color = 'HECRAS', shape = 'HECRAS'), size = 3) + 
  geom_point(aes(x = name, y = MWR, color = 'MWR', shape = 'MWR'), size = 3) + 
  geom_point(aes(x = name, y = rowMeans(cbind(KS, HECRAS, MWR))), color = 'black', size = 2) + 
  labs(x = '', y = 'Manning\'s Roughness Coefficient', color = 'Source', shape = 'Source') + 
  scale_y_origin(breaks = seq(0, 1, 0.05), minor_breaks = seq(0, 1, 0.05)) + 
  scale_shape_manual(values = 15:18) + 
  scale_color_manual(values = c('#800000', '#f58231', '#000075', '#4389d8')) + 
  coord_flip(clip = 'off') + theme(panel.grid.major.x = element_line(color = 'grey90'))
manning_values <- manning %>% 
  mutate(values = rowMeans(cbind(KS, HECRAS, MWR))) %>% 
  dplyr::select(code, values)
manning_values[1,2] <- 0.035
# manning_values <- manning_values %>% 
#   mutate(values = cbind(0.035, values) %>% apply(1, max))

## change LULC codes to roughness values
lulc.n <- lulc.n %>% 
  reclassify(cbind(NA, 0)) %>%
  reclassify(manning_values)

## reformat raster to match DEM
lulc.dem <- projectRaster(lulc.n, blank)
# range(lulc.dem[])

## save out
writeRaster(lulc.dem, format = 'ascii', overwrite = TRUE, 
            filename = 'C:/Users/cbowers/Desktop/russian.n.asc')

```

```{r}
## save all rasters as an .Rdata file
# save(dem, width, lulc.dem, file = 'C:/Users/cbowers/Desktop/LISFLOOD/raster_files.Rdata')
load('C:/Users/cbowers/Desktop/LISFLOOD/raster_files.Rdata')

```


```{r}
## step 4) generate startfile

## find the most relevant gauges
param <- c('00060', '00065'); names(param) <- c('discharge_cfs', 'gageht_ft')
statcode <- c('00001', '00002', '00003', '00008'); names(statcode) <- c('max', 'min', 'mean', 'median')
sites <- whatNWISsites(stateCd = 'CA', parameterCD = param, hasDataTypeCd = 'dv') %>% 
  subset(str_length(paste(site_no)) == 8) %>% 
  st_as_sf(coords = c('dec_long_va', 'dec_lat_va'), crs = st_crs(california)) %>% 
  st_intersection(california %>% subset(NAME %in% c('Sonoma', 'Mendocino'))) %>% 
  subset(grepl('RUSSIAN', station_nm)) %>% 
  st_intersection(california %>% subset(NAME == 'Sonoma')) %>%  #subset to gauges below reservoirs
  subset(site_no != 11457002) %>%  #subset to gauges with cfs only
  subset(!(site_no %in% c(11463980, 11465390)))  #keep gauges with long records only
ggplot() + 
  geom_sf(data = sonoma %>% st_transform(crs_dem), color = 'grey70') + 
  geom_sf(data = aoi, fill = 'black', alpha = 0.1) +
  geom_sf(data = russian %>% st_crop(sonoma) %>% st_transform(crs_dem)) + 
  geom_sf(data = sites %>% st_transform(crs_dem), aes(color = site_no), size = 3) + 
  theme_void()

```

```{r}
## find baseflow
data <- readNWISdv(11463500, parameterCd = param, startDate = '2000-01-01') %>% 
  renameNWISColumns %>% 
  mutate(flow_m3s = Flow/(mft^3))
timeseries <- data %>% 
  group_by(Date) %>% 
  summarize(flow_m3s = mean(flow_m3s), .groups = 'drop') %>% 
  filter(month(Date) %in% c(10:12, 1:4)) %>%
  .$flow_m3s 
means <- c(); medians <- c()
for (i in 1:60) {
  means[i] <- lfstat::baseflow(timeseries, block.len = i) %>% Mean
  medians[i] <- lfstat::baseflow(timeseries, block.len = i) %>% median(na.rm = TRUE)
}
ggplot() + 
  geom_line(aes(x = 1:60, y = means, color = 'mean'), size = 1) + 
  geom_line(aes(x = 1:60, y = medians, color = 'median'), size = 1) + 
  geom_hline(yintercept = 3:4, linetype = 'dashed') + 
  scale_x_origin() + scale_y_origin() + theme_bw()
means; medians

```

####################################

run LISFLOOD parameter testing in Sherlock

constant parameters: 

  * n <- 1000  #number of simulations
  * simlength <- 30*24*3600  #simulation length (s)
  * spinup <- 15*24*3600  #simulation spin-up time (s)
  * baseflow <- 3  #baseflow (m3/s)
  * Qp <- 112000 / (mft^3)  #m3/s  
  
variable parameters:

  * SGCn = qunif(x1, min = 0.015, max = 0.075)  #channel roughness
  * tp = qunif(x2, min = 0, max = 200)  #time to peak flow (hrs)
  * m = qunif(x3, min = 0, max = 10)  #hydrograph shape parameter
  * edge = qunif(x4, min = 10, max = 25)  #inflow channel width (m)
  
```{r obs}
#### load observed floodplain #### 

## load dem
load('C:/Users/cbowers/Desktop/dem_save.Rdata')
# res(dem)

# ## load 100-year floodplain
# NFHL <- st_read('D:/Research/_gis/California/_floodhazard/NFHL_06_20190810/S_Fld_Haz_Ar.shp', quiet = TRUE) %>%
#   st_transform(6417)
# floodzone <- function(x) {
#   if (x %in% c('A', 'A99', 'AE', 'AH', 'AO')) {
#     return('YES')
#   } else if (x %in% c('V', 'VE')) {
#     return('WAVE')
#   } else if (x %in% c('D', 'X')) {
#     return('NO')
#   } else if (x == 'OPEN WATER') {
#     return('WATER')
#   } else {
#     return(NA)
#   }
# }
# NFHL <- NFHL %>%
#   mutate(FLOODPLAIN = factor(apply(data.frame(NFHL$FLD_ZONE), 1, function(x) floodzone(x)))) %>%
#   dplyr::select(FLOODPLAIN, geometry) %>%
#   subset(FLOODPLAIN == 'YES') %>%
#   mutate(NFHL = 1)
# 
# ## get rid of additional floodplain pixels
# remove.pixels <-
#   st_read('D:/Research/_gis/California/_hydrology/nhd_majorriversandcreeks/MajorRiversAndCreeks.shp',
#           quiet = TRUE) %>% st_zm %>%
#   st_transform(4269) %>%
#   st_crop(sonoma) %>%
#   filter(GNIS_Name %in% c('Dry Creek', 'Mark West Creek', 'Austin Creek')) %>%
#   filter(!(OBJECTID %in% c(1294,1297,1298,42552,106984,1263,1264,
#                            106986,20379,57388,1653,1652,116351))) %>%
#   st_transform(6417) %>%
#   st_union %>%
#   st_buffer(dist = 250) %>%
#   st_difference(russian %>% st_transform(6417) %>% st_buffer(500) %>% st_union) %>%
#   as('Spatial') %>%
#   rasterize(dem)
# 
# ## create raster of observed values
# obs.full <- NFHL %>%
#   dplyr::select(NFHL) %>%
#   st_transform(6417) %>%
#   st_cast('POLYGON') %>%
#   st_crop(aoi) %>%
#   as('Spatial') %>%
#   rasterize(dem, getCover = TRUE)
# obs.full <- obs.full > 0.5
# obs <- obs.full %>% overlay(remove.pixels, fun = function(x, y) ifelse(is.na(y), x, 0))

## save out values
# save(NFHL, obs, obs.full, remove.pixels, file = 'C:/Users/cbowers/Desktop/NFHL.Rdata')
load('C:/Users/cbowers/Desktop/NFHL.Rdata')

```

```{r}
#### load simulated floodplain ####

## find best-fit simulation
sim.list <- 
  list.files('C:/Users/cbowers/Desktop/LISFLOOD/sonoma_sherlock/21-05-27 rp100/results') %>% 
  gsub('rpflow', '', .) %>% gsub('.max', '', .) %>% toNumber

num_cores <- 5
pb <- txtProgressBar(min = 0, max = length(sim.list), style = 3)
cl <- parallel::makeCluster(num_cores)
registerDoSNOW(cl)
accuracy <-
  foreach(i = sim.list, .combine = 'rbind',
    .packages = c('raster', 'dplyr'),
    .options.snow = list(progress = function(n) setTxtProgressBar(pb, n))) %dopar% {
# accuracy <- data.frame(id = NA, hitrate = NA, falsealarm = NA, fstat = NA, bias = NA)[-1,]
# for (i in sort(sim.list)) {
      sim <-
        paste0('C:/Users/cbowers/Desktop/LISFLOOD/sonoma_sherlock/21-05-27 rp100/results/rpflow',
               i, '.max') %>% raster %>%
        overlay(dem, fun = function(x,y) ifelse(y>1, x, NA))
      temp <- obs %>% 
        overlay(sim, fun = function(x,y) {
          ifelse(x > 0 & y > 0, 0, ifelse(
            x > 0 & y <= 0, -1, ifelse(
              x <= 0 & y > 0, 1, NA)))})
      
      tb <- table(temp[])
      # accuracy[i,] <- 
        c(id = i, 
        hitrate = unname(tb[2] / sum(tb[1:2])),
        falsalarm = unname(tb[3] / sum(tb[2:3])),
        fstat = unname(tb[2] / sum(tb)),
        bias = unname(tb[3] / tb[1]))
      # setTxtProgressBar(pb, i)
    }
stopCluster(cl)

samples <-
  read.table('C:/Users/cbowers/Desktop/LISFLOOD/sonoma_sherlock/21-05-27 rp100/samples_rp100.txt',
             header = TRUE) %>%
  mutate(id = 1:nrow(.)) %>% 
  left_join(data.frame(accuracy), by = 'id')

g <- samples %>% 
  mutate(bias.odds = bias / (1 + bias)) %>% 
  ggplot() + 
  geom_point(aes(x = fstat, y = bias.odds, color = id)) + 
  geom_hline(yintercept = 0.5, linetype = 'dashed') + 
  geom_vline(xintercept = 1, linetype = 'dashed')
plotly::ggplotly(g)

samples <- samples %>% 
  mutate(bias.odds = bias / (1 + bias)) %>% 
  mutate(good = case_when(
    fstat > 0.68 ~ TRUE,
    bias.odds > 0.45 & bias.odds < 0.55 & fstat > 0.65 ~ TRUE))

```

```{r}
#1D
ggplot(samples) + geom_point(aes(x = SGCn, y = fstat, color = good)) + 
  scale_color_manual(values = baker[5], na.value = 'grey80')
ggplot(samples) + geom_point(aes(x = tp, y = fstat, color = good)) + 
  scale_color_manual(values = baker[5], na.value = 'grey80')
ggplot(samples) + geom_point(aes(x = m, y = fstat, color = good)) + 
  scale_color_manual(values = baker[5], na.value = 'grey80')
ggplot(samples) + geom_point(aes(x = edge, y = fstat, color = good)) + 
  scale_color_manual(values = baker[5], na.value = 'grey80')

#2D
ggplot(samples) + geom_point(aes(x = SGCn, y = tp, color = good)) + 
  scale_color_manual(values = baker[5], na.value = 'grey80')
ggplot(samples) + geom_point(aes(x = SGCn, y = m, color = good)) + 
  scale_color_manual(values = baker[5], na.value = 'grey80')
ggplot(samples) + geom_point(aes(x = SGCn, y = edge, color = good)) + 
  scale_color_manual(values = baker[5], na.value = 'grey80')
ggplot(samples) + geom_point(aes(x = tp, y = m, color = good)) + 
  scale_color_manual(values = baker[5], na.value = 'grey80')
ggplot(samples) + geom_point(aes(x = tp, y = edge, color = good)) + 
  scale_color_manual(values = baker[5], na.value = 'grey80')
ggplot(samples) + geom_point(aes(x = m, y = edge, color = good)) + 
  scale_color_manual(values = baker[5], na.value = 'grey80')

## conclusions: SGCn and edgewidth matter more than tp and m
## (which is weird, tp should definitely matter)
# g <- ggplot(samples) + geom_point(aes(x = SGCn, y = edge, fill = id, color = good)) + 
#   scale_color_manual(values = baker[5], na.value = 'grey80')
# plotly::ggplotly(g)

ggplot() + 
  geom_point(data = samples, aes(x = SGCn, y = edge, color = fstat)) + 
  geom_label(data = samples %>% filter(good), 
             aes(x = SGCn, y = edge, label = id, color = fstat)) + 
  geom_hline(yintercept = mean(edge.in$layer), linetype = 'dashed') +  
  scale_color_scico(palette = 'lajolla', limits = c(0.65, NA), na.value = NA) + 
  coord_cartesian(xlim = c(0.02, 0.04), ylim = c(22,25))
ggplot(samples %>% filter(good)) + 
  geom_point(data = samples, aes(x = SGCn, y = edge, color = bias)) + 
  geom_label(aes(x = SGCn, y = edge, label = id, color = bias)) + 
  geom_hline(yintercept = mean(edge.in$layer), linetype = 'dashed') +  
  scale_color_scico(palette = 'berlin', limits = c(0, 2), na.value = NA) + 
  coord_cartesian(xlim = c(0.02, 0.04), ylim = c(22,25))

g <- ggplot(samples) +
  geom_point(aes(x = SGCn, y = edge, color = id)) +
  geom_hline(yintercept = mean(edge.in$layer), linetype = 'dashed') +
  coord_cartesian(xlim = c(0.02, 0.04), ylim = c(22,25))
plotly::ggplotly(g)

samples %>% filter(id %in% c(602,47,897))

## final decision: use the "true" edgewidth & SGCn = 0.0275

## note: all rp100 simulations were run with a truncated russian.n.asc (min=0.035),
## but since 0.0275 < the true min (0.031) things should end up the same

## go wtih id = 678 as the winner

```


```{r}
# ggplot() + 
#   geom_sf(data = sonoma %>% st_transform(6417), color = 'grey70', fill = 'grey90') + 
#   geom_sf(data = russian %>% st_crop(sonoma) %>% st_transform(6417)) + 
#   geom_raster(data = raster.df(dem), aes(x = x, y = y), fill = 'red', alpha = 0.15) + 
#   geom_sf(data = temp) + 
#   geom_sf(data = temp %>% filter(site_no %in% c(gauges, stages)), color = 'red')
# 
# rivers <- st_read('./_gis/California/_hydrology/nhd_majorrivers/MajorRivers.shp', quiet = TRUE) %>% 
#   st_zm(st_transform(albers)) 
# creeks <- st_read('./_gis/California/_hydrology/nhd_majorriversandcreeks/MajorRiversAndCreeks.shp', quiet = TRUE) %>% 
#   st_zm(st_transform(albers)) 
# russian <- rivers %>% 
#   subset(grepl('Russian', GNIS_Name))
# 
# rivers <- rivers %>% st_transform(st_crs(sonoma)) %>% st_crop(sonoma)
# creeks <- creeks %>% st_transform(st_crs(sonoma)) %>% st_crop(sonoma)
# 
# ggplot() + 
#   geom_sf(data = sonoma %>% st_transform(crs(dem)), color = 'grey70', fill = 'grey90') + 
#   geom_sf(data = russian %>% st_crop(sonoma), color = ggcolor(4)[4]) + 
#   geom_sf(data = rivers %>% 
#             filter(grepl('Russian', GNIS_Name)) %>% 
#             st_transform(crs(dem)) %>% st_crop(dem), 
#           aes(color = GNIS_Name), size = 1) + 
#   geom_sf(data = creeks %>% 
#             filter(grepl('Dry', GNIS_Name) | grepl('Mill', GNIS_Name) | grepl('Mark', GNIS_Name)) %>% 
#             st_transform(crs(dem)) %>% st_crop(dem),
#           aes(color = GNIS_Name), size = 1) + 
#   geom_raster(data = raster.df(dem), aes(x = x, y = y), fill = 'grey50', alpha = 0.15) + 
#   geom_sf(data = temp, size = 1.5, color = 'black') + 
#   geom_sf(data = temp, size = 1, color = 'grey80') + 
#   geom_sf(data = temp %>% filter(site_no %in% c(gauges, stages)), size = 1.5, color = 'red') + 
#   geom_sf(data = temp %>% filter(site_no %in% c(gauges, stages)), size = 1, color = 'black') + 
#   theme_void()
# ggsave('C:/Users/cbowers/Desktop/test.jpg', height = 6)
  

```

